Untitled

### 2024-01-29 Evalsims.Rmd
hey

method_names <- c("HistCAL-CP (5 bins)", "Conditional-CP", "SC-CP (ours)", "Unconditional-CP", "Mondrian-CP (5 bins)", "Oracle")
names(method_names) <- c("cal_binning_1", "conditional", "isotonic","marginal", "mondrian_1", "oracle")

out <- out[out$method %in% c("cal_binning_1", "mondrian_1", "marginal", "isotonic", "conditional", "oracle")]

@@

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Conditional-CP" , "Unconditional-CP", "HistCAL-CP (5 bins)", "Mondrian-CP (5 bins)", "Oracle")  )

@@

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
method_names <- c("HistCAL (5 bins)", "Conditional-CP", "SC-CP (ours)", "Unconditional-CP", "Mondrian-CP (5 bins)", "Oracle")
names(method_names) <- c("cal_binning_5", "conditional", "isotonic","marginal", "mondrian_5", "oracle")

@@

out <- out[out$method %in% c("oracle", "cal_binning_5", "mondrian_5", "marginal", "isotonic", "conditional")]
out$method <- method_names[match(out$method, names(method_names))]

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Conditional-CP" , "Unconditional-CP", "HistCAL (5 bins)", "Mondrian-CP (5 bins)", "Oracle")  )

plot1 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))

plot2 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))

library(patchwork)
combined_plot <- plot1 + plot2 + plot_layout(guides = "collect") & theme(legend.position = "")
combined_plot
print(combined_plot)

>>>>

method_names <- c("HistCAL-CP (5 bins)", "Cond-CP", "SC-CP (ours)", "Uncond-CP", "Mondrian-CP", "Oracle")
names(method_names) <- c("cal_binning_1", "conditional", "isotonic","marginal", "mondrian_1", "oracle")

out <- out[out$method %in% c("mondrian_1", "marginal", "isotonic", "conditional", "oracle")]

@@

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Cond-CP" , "Uncond-CP", "HistCAL-CP (5 bins)", "Mondrian-CP", "Oracle")  )

@@

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
method_names <- c("HistCAL (5 bins)", "Cond-CP", "SC-CP (ours)", "Uncond-CP", "Mondrian-CP", "Oracle")
names(method_names) <- c("cal_binning_5", "conditional", "isotonic","marginal", "mondrian_1", "oracle")

@@

out <- out[out$method %in% c("oracle",   "mondrian_1", "marginal", "isotonic", "conditional")]
out$method <- method_names[match(out$method, names(method_names))]

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Cond-CP" , "Uncond-CP", "HistCAL (5 bins)", "Mondrian-CP", "Oracle")  )

plot1 <- ggplot(out , aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw() + labs(y = TeX("Coverage ($\\alpha = 0.1$)"), x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))  +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed") + geom_hline(yintercept = 0.9, alpha = 0.5, color = "red")

plot2 <- ggplot(out , aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(y = "Interval Width", x = TeX("Quintiles of $\\sigma^2(X)$")) + scale_x_discrete(labels = c("Q.1", 
                                                       "Q.2",
                                                       "Q.3",
                                                       "Q.4",
                                                       "Q.5",
                                                       "Uncond."))   +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank()))  + geom_vline(xintercept = 5.5, alpha = 0.3, linetype = "dashed")

library(patchwork)
combined_plot <- plot1 + plot2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
combined_plot
print(combined_plot)

### 2024-01-29 plot_curves.Rmd
hey

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.5.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "Isotonic", "method"] <- "SC-CP (ours)"
#data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
#data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "Conditional (kernel)", "method"] <- "Conditional-CP"
data[data$method == "Marginal", "method"] <- "Unconditional"

@@

data$method <- factor(data$method, levels = c("SC-CP (ours)", "Conditional-CP", "Unconditional"))

>>>>

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.5.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "isotonic", "method"] <- "SC-CP (ours)"
#data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
#data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "conditional", "method"] <- "Cond-CP"
data[data$method == "marginal", "method"] <- "Uncond-CP"

@@

data$method <- factor(data$method, levels = c("SC-CP (ours)", "Cond-CP", "Uncond-CP"))
